\plaintitle

### 2017-06-05 papers/IoT2017/solution.tex
no message

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\bid} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\label{fig:sellFlow}
\end{figure*}

@@

Now, the prosumer can engage in energy trading anonymously.
To find a trade partner, it can either post an \emph{energy bid} on the bid storage, or simply search the storage for an acceptable \emph{energy ask}.
To post an energy bid, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
It can then post the energy bid \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
If another prosumer, who would like to buy energy, finds the bid acceptable, it can contact the selling prosumer at the communication address given by the bid.

@@

Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted consumption assets might be used to trade excessive amounts.

Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
After transferring the assets through a mixing service, the prosumer is ready to post an energy ask on the bid service.
To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy ask, which includes an anonymous communication address.
If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
which credits the energy amount to the prosumer, for billing purposes.
Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.

>>>>

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\label{fig:sellFlow}
\end{figure*}

@@

Now, the prosumer can engage in energy trading anonymously.
To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
It can then post the energy ask \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication address given by the ask.

@@

Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.

Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication address.
If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
which credits the energy amount to the prosumer, for billing purposes.
Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.
